---
title: "Week 2 Assignment"
author: "Nabila Hossain"
date: "July 12, 2015"
output:
  html_document:
    keep_md: yes
---

_Assignment: R has built in functions for `choose()` and `factorial()`. Your task is to write your own variation of the `choose()`._

I wrote the code below to find "n choose r" without using the built in functions `choose()` and `factorial()` in __R__.

The code below will work for any positive number for $n$ and $r$ where $n\ge{r}$ to produce answer for the function: 
$$\binom nr = \frac{n!}{(n-r)!r!}$$
 

```{r}
k <- function (n, r) { 

  a <- 1
  b <- 1
  d <- 1

  e <- n - r 

  for (x in 1:n) {
    a <- a*((1:n)[x]) 
    } 
  
  for (y in 1:r) {
    b <- b*((1:r)[y]) 
    } 

  for (z in 1:e) {
    d <- d*((1:e)[z]) 
    } 

  l = (a / (d * b))
  print(l) 
}
```

Using the code we find __"3 choose 2"__ or $(^3 _2)$:
```{r}
k(3,2)
```

If we use the equation $\binom nr = \frac{n!}{(n-r)!r!}$ we find that __"3 choose 2"__ equals $3$.
$$\binom {3}{2} = \frac{3!}{(3-2)!2!} =\frac{3{*}2}{1{*}2} = 3$$


Using the code we find __"6 choose 3"__ or $(^6 _3)$:
```{r}
k(6,3)
```

If we use the equation we find that __"6 choose 3"__ equals $20$.
$$\binom {6}{3} = \frac{6!}{(6-3)!3!} =\frac{6*5*4*{3!}}{3!{*}3!} = \frac{6{*}5{*}4}{3{*}2}= \frac{5{*}4}{1}=20$$

Using the code we can also find large numbers like $(^{30} _9)$:
```{r}
k(30,9)
```

